Light inextensible strings under tension in the Schwarzschild geometry

### 2019-02-07 string_ajp.tex
include radius of curvature switch figure

\begin{figure}[h!] % Created by "flamm.R"
\centering
\includegraphics[width=70mm]{flamm_string.pdf}
\caption{Perspective fiew of Flamm's paraboloid with superimposed minimal-length
  path corresponding to a taut, light string}
\label{flamm}
\end{figure}

@@

\noindent which would give~$R$ as a function of~$\left(r,r'\right)$.
Considering~$r'(\phi)=0$ shows that if a string is tangential at a
point with~$r_0>1$, then it has a radius of curvature of~$r_0^2$ at
that point.  Any circular path, including a circular orbit at~$r=r_0$,
has a radius of curvature of $r_0<r_0^2$, showing that circular orbits
cannot follow a taut string at closest approach.  Also observe that
null geodesics have a radius of curvature of $2r_0^2/3 < r_0^2$,
showing that light cannot follow a taut string at closest approach
either.

@@

\section{Results}
Solutions to equation~\ref{rdashdash} fall into two distinct classes:
those with $r>1$ at all points, and those which attain $r=1$, in which
case the string is tangential to the event horizon, in general.
Numerical methods show that if the closest approach is greater than a
critical value of~$\simeq 1.076109317(1)$, the string does not
self-intersect (Figure~\ref{closest_approach_non_self_intersecting});
if the closest approach is less than this value, the then string
crosses itself at~$\phi=\pi/2$
(Figure~\ref{closest_approach_self_intersecting}).  The case where the
string is tangent to the event horizon at~$r=1,\phi=0$ is shown in
Figure~\ref{fixed_EH_intersection}.

@@

\begin{figure}[h!] % created by "closest_approach2.R"
\centering
\includegraphics[width=170mm]{closest_approach_selfintersecting.pdf}
\caption{Strings arranged by closest approach to the event horizon:
 self-intersecting strings shown for $\phi\geq 0$}
\label{closest_approach_self_intersecting}
\end{figure}

@@

>>>>

\begin{figure}[h!] % Created by "flamm.R"
\centering
\includegraphics[width=70mm]{flamm_string.pdf}
\caption{Perspective view of Flamm's paraboloid with superimposed minimal-length
  path corresponding to a taut, light string}
\label{flamm}
\end{figure}

@@

\noindent which would give~$R$ as a function of~$\left(r,r'\right)$.
Considering~$r'(\phi)=0$ shows that if a string is tangential at a
point with~$r_0>1$, then it has a radius of curvature of~$r_0^2$ at
that point.  Any circular path, including a circular orbit at~$r=r_0$,
has a radius of curvature of $r_0<r_0^2$, showing that circular orbits
cannot follow a taut string at closest approach.  Also observe that
null geodesics have a radius of curvature of $2r_0^2/3 < r_0^2$,
showing that light cannot follow a taut string at closest approach
either.  The string has a point of inflection
if~$\left(r'\right)^2=2r(r-1)$.

@@

\section{Numerical results}

Solutions to equation~\ref{rdashdash} fall into two distinct classes:
those with $r>1$ at all points, and those which attain $r=1$, in which
case the string is tangential to the event horizon, in general.
Numerical methods show that if the closest approach is greater than a
critical value of~$\simeq 1.076109317(1)$, the string does not
self-intersect (Figure~\ref{closest_approach_non_self_intersecting});
if the closest approach is less than this value, the then string
crosses itself at~$\phi=\pi/2$
(Figure~\ref{closest_approach_self_intersecting}).  The case where the
string is tangent to the event horizon at~$r=1,\phi=0$ is shown in
Figure~\ref{fixed_EH_intersection}.

@@

\begin{figure}[h!] % created by "closest_approach2.R"
\centering
\includegraphics[width=170mm]{closest_approach_selfintersecting.pdf}
\caption{Self-intersecting strings arranged by closest approach to the
  event horizon which occurs at $\phi=0$.  
  shown for $\phi\geq 0$}
\label{closest_approach_self_intersecting}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics{curvature_switch.pdf} % created by "radius_of_curvature_switch.R"
\caption{Strings arranged by point of curvature switch, which occurs
  at~$\phi=0$.  Colour changes from black to red at points of
  infinite~$R$; black indicates convex to the origin and red indicates
  concave regions}
\label{curvature_switch}
\end{figure}
